---
title: "Solve a problem in computing the area of each polygon inside a buffer"
author: "Loïc Davadan"
date: 2018-06-14
output: html_document
---
```{r include=FALSE}
load("~/Documents/code/agromet-tests/env_clc.RData")
```

In the context of the AGROMET project, we searched to include data from CORINE land cover in our models. I refer you to my post [How to get CORINE land cover data from Wallonia](https://ldavadan.github.io/post/get_corinelc_wallonia/) where I explained how we got data and how we reclass land covers in groups.

During my work, I wanted to calculate the part of each land cover around every station and I am arrived at a problem.

# Explanation of the method and emerging problem

First, as I explained it in my precedent post, I imported data from CORINE land cover and its legend. I transformed the legend to make a few classes more congruent with our project. And then, I imported all the stations.

Once that was done, I have made spatial transformations and verified the CRS (Coordinate Reference System) of each data. Lambert 2008 is the CRS we need four our spatial projections.

Then, the objective was to observe the different land covers around each station. That's why I created a buffer around each station with a distance of 100 meters.

Then, I made some manipulations to extract the land covers which are around the stations et compute the part of each of them. And here is the problem ! 4 stations had an agricultural area near to them but its prevalence inside the buffer was __159%__ !!

# Investigation to find the error

## Searching which polygon is problematic

I checked every step of my code to find where appears the error. I found a polygon which appears 4 times whereas all other polygons appear only once. I observed it with `mapview` to check if this polygon was the one which appears on the 4 different stations. And this polygon was the one which is problematic.

```{r echo=FALSE}
library(mapview)
mapview(guilty, col.regions = "orange") + stations.buff.sf
```

Then, I looked for the step where a computation was done on this polygon. Once it was found, I understood it was because of the ID of the polygon which was appearing 4 times and then, a computation was done on it. For that reason, I made a new ID that was named customID to attribute 4 ID to this polygon, one for each appearance. Then, the computation was correctly done and the percentage was correct.


# Conclusion

Investigate to find an error in the code is a very important part. It has to be methodic, examining every line of code, understanding every computation, and finding solutions and alternatives. That requires to look for documentation. It was a very formative exercise.




